# Ambulances


Find this notebook on the web at
<a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/resampling_method.html#nte-ambulances">Note <span>2.1</span></a>.

**Note: Comments in code**

The first thing to say about the code you will see below is there are
some lines that do not do anything; these are the lines beginning with a
`#` character (read `#` as “hash”). Lines beginning with `#` are called
*comments*. When R sees a `#` at the start of a line, it ignores
everything else on that line, and skips to the next. Here’s an example
of a comment:

```{r}
# R will completely ignore this text.
```

Because R ignores lines beginning with `#`, the text after the `#` is
just for us, the humans reading the code. The person writing the code
will often use comments to explain what the code is doing.

**End of Note: Comments in code**

Our next task is to use R to simulate a single day of ambulances. We
will again represent each ambulance by a random number from 0 through 9.
16 of these numbers represents a simulation of all 16 ambulances
available to the contractor. We call a simulation of all ambulances for
a specific day — one *trial*.

Recall that we want 16 10-sided dice — one per ambulance. Our dice
should be 10-sided, because each ambulance has a 1-in-10 chance of being
out of order.

The program to simulate one trial of the ambulances problem therefore
begins with these commands:

```{r}
# Ask R to generate 16 numbers from 0 through 9.

# These are the numbers we will ask R to select from.
numbers <- c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9)

# Get 16 values from the *numbers* sequence.
# Store the 16 numbers with the name "a"
# We will explain the replace=TRUE later.
a <- sample(numbers, 16, replace=TRUE)

# The result is a sequence of 16 numbers.
a
```

The commands above ask the computer to store the results of the random
drawing in a location in the computer’s memory to which we give a name
such as `a` or `ambulances` or `aardvark` — the name is up to us.

Next we need to count the number of defective ambulances:

```{r}
# Count the number of nines in the random numbers.
# The "a == 9" part identifies all the numbers equal to 9.
# The "sum" part counts how many numbers "a == 9" found.
b <- sum(a == 9)
# Show the result
b
```



Notice that the code above is *exactly* the same as the code we built up
in steps. But notice too, that the answer we got from this code was
slightly different from the answer we got first.

Why did we get a different answer from the same code? See if you can
come up with a good answer before reading the explanation below.

**Note: Randomness in estimates**

This is an essential point — our code uses *random numbers* to get an
*estimate* of the quantity we want — in this case, the probability of
three or more ambulances being out of order. Every run of our code block
above will use a different set of random numbers. Therefore, every run
of the code will give us a very slightly different number. As you will
soon see, we can make our estimate more and more accurate, and less and
less different between each run, by doing many trials in each run. Here
we did 1000 trials, but we will usually do 10000 trials, to give us a
good estimate, that does not vary much from run to run.

**End of Note: Randomness in estimates**

Don’t worry about the detail of how each of these commands works — we
will cover those details gradually, over the next few chapters. But, we
hope that you can see, in principle, how each of the operations that the
computer carries out are analogous to the operations that you yourself
executed when you solved this problem using the ten-sided dice. This is
exactly the procedure that we will use to solve every problem in
probability and statistics that we must deal with.

While writing programs like these take a bit of getting used to, it is
vastly simpler than the older, more conventional approaches to such
problems routinely taught to students.

## 2.4 How resampling differs from the conventional approach

In the standard approach the student learns to choose and solve a
formula. Doing the algebra and arithmetic is quick and easy. The
difficulty is in choosing the correct formula. Unless you are a
professional statistician, it may take you quite a while to arrive at
the correct formula — considerable hard thinking, and perhaps some
digging in textbooks. More important than the labor, however, is that
you may come up with the wrong formula, and hence obtain the wrong
answer. And how would you know if you were wrong?

Most students who have had a standard course in probability and
statistics are quick to tell you that it is not easy to find the correct
formula, even immediately after finishing a course (or several courses)
on the subject. After leaving school or university, it is harder still
to choose the right formula. Even many people who have taught statistics
at the university level (including this writer) must look at a book to
get the correct formula for a problem as simple as the ambulances, and
then we are often still not sure we have the right answer. This is the
grave disadvantage of the standard approach.

In the past few decades, resampling and other Monte Carlo simulation
methods have come to be used extensively in scientific research. But in
contrast to the material in this book, simulation has mostly been used
in situations so complex that mathematical methods have not yet been
developed to handle them. Here are examples of such situations:



1.  Imagine a large train station such as Grand Central Terminal in New
    York or King’s Cross in London. We are responsible for planning the
    new station layout so that passengers can move as quickly as
    possible to and from their trains in rush-hour. It will likely be
    far too complicated to make formulas to represent the passenger
    flows, but we could use the computer to simulate passengers, and
    their movements, and try different potential layouts within the
    simulation.

2.  The Navy might want to know how long the average ship will have to
    wait for dock facilities. The time of completion varies from ship to
    ship, and the number of ships waiting in line for dock work varies
    over time. This problem can be handled quite easily with the
    experimental simulation method, but formal mathematical analysis
    would be difficult or impossible.

3.  What are the best tactics in baseball? Should one bunt? Should one
    put the best hitter up first, or later? By trying out various
    tactics with dice or random numbers, Earnshaw Cook (in his book
    *Percentage Baseball*), found that it is best never to bunt, and the
    highest-average hitter should be put up first, in contrast to usual
    practice. Finding this answer would have been much more difficult
    with the analytic method.



4.  Which search pattern will yield the best results for a ship
    searching for a school of fish? Trying out “models” of various
    search patterns with simulation can provide a fast answer.

5.  What strategy in the game of Monopoly will be most likely to win?
    The simulation method systematically plays many games (with a
    computer) testing various strategies to find the best one.

But those five examples are all complex problems. This book and its
earlier editions break new ground by using this method for *simple
rather than complex problems*, especially in statistics rather than pure
probability, and in teaching *beginning rather than advanced* students
to solve problems this way. (Here it is necessary to emphasize that the
resampling method is used to *solve the problems themselves rather than
as a demonstration device to teach the notions found in the standard
conventional approach*. Simulation has been used in elementary courses
in the past, but only to demonstrate the operation of the analytical
mathematical ideas. That is very different than using the resampling
approach to solve statistics problems themselves, as is done here.)

Once we get rid of the formulas and tables, we can see that statistics
is a matter of *clear thinking, not fancy mathematics*. Then we can get
down to the business of learning how to do that clear statistical
thinking, and putting it to work for you. *The study of probability* is
purely mathematics (though not necessarily formulas) and technique. But
*statistics has to do with meaning*. For example, what is the meaning of
data showing an association just discovered between a type of behavior
and a disease? Of differences in the pay of men and women in your firm?
Issues of causation, acceptability of control, and design of experiments
cannot be reduced to technique. This is “philosophy” in the fullest
sense. Probability and statistics calculations are just one input.
Resampling simulation enables us to get past issues of mathematical
technique and focus on the crucial statistical elements of statistical
problems.

We hope you will find, as you read through the chapters, that the
resampling way of thinking is a good way to think about the more
traditional statistical methods that some of you may already know. Our
approach will be to use resampling to understand the ideas, and then
apply this understanding to reason about traditional methods. You may
also find that the resampling methods are not only easier to understand
— they are often more useful, because they are so general in their
application.

<div class="hidden" id="quarto-navigation-envelope">
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar-title">Resampling statistics</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-navbar-title">Resampling statistics</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-next"><span class="chapter-number">3</span> 
<span class="chapter-title">What is probability?</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-prev"><span class="chapter-number">1</span> 
<span class="chapter-title">Introduction</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/index.html{{&lt;-var-lang-&gt;}}-version">R
version</span> <span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/preface_third.htmlPreface-to-the-third-edition">Preface
to the third edition</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/preface_second.htmlPreface-to-the-second-edition">Preface
to the second edition</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/intro.html&lt;span-class='chapter-number'&gt;1&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Introduction&lt;/span&gt;"><span class="chapter-number">1</span> 
<span class="chapter-title">Introduction</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/resampling_method.html&lt;span-class='chapter-number'&gt;2&lt;/span&gt;--&lt;span-class='chapter-title'&gt;The-resampling-method&lt;/span&gt;"><span class="chapter-number">2</span> 
<span class="chapter-title">The resampling method</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/what_is_probability.html&lt;span-class='chapter-number'&gt;3&lt;/span&gt;--&lt;span-class='chapter-title'&gt;What-is-probability?&lt;/span&gt;"><span class="chapter-number">3</span> 
<span class="chapter-title">What is probability?</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/about_technology.html&lt;span-class='chapter-number'&gt;4&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Introducing-{{&lt;-var-lang-&gt;}}-and-the-Jupyter-notebook&lt;/span&gt;"><span class="chapter-number">4</span> 
<span class="chapter-title">Introducing R and the Jupyter
notebook</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/resampling_with_code.html&lt;span-class='chapter-number'&gt;5&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Resampling-with-code&lt;/span&gt;"><span class="chapter-number">5</span> 
<span class="chapter-title">Resampling with code</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/resampling_with_code2.html&lt;span-class='chapter-number'&gt;6&lt;/span&gt;--&lt;span-class='chapter-title'&gt;More-resampling-with-code&lt;/span&gt;"><span class="chapter-number">6</span> 
<span class="chapter-title">More resampling with code</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/sampling_tools.html&lt;span-class='chapter-number'&gt;7&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Tools-for-samples-and-sampling&lt;/span&gt;"><span class="chapter-number">7</span> 
<span class="chapter-title">Tools for samples and sampling</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/probability_theory_1a.html&lt;span-class='chapter-number'&gt;8&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Probability-Theory,-Part-1&lt;/span&gt;"><span class="chapter-number">8</span> 
<span class="chapter-title">Probability Theory, Part 1</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/probability_theory_1b.html&lt;span-class='chapter-number'&gt;9&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Probability-Theory-Part-1-(continued)&lt;/span&gt;"><span class="chapter-number">9</span> 
<span class="chapter-title">Probability Theory Part 1
(continued)</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/more_sampling_tools.html&lt;span-class='chapter-number'&gt;10&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Two-puzzles-and-more-tools&lt;/span&gt;"><span class="chapter-number">10</span> 
<span class="chapter-title">Two puzzles and more tools</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/probability_theory_2_compound.html&lt;span-class='chapter-number'&gt;11&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Probability-Theory,-Part-2:-Compound-Probability&lt;/span&gt;"><span class="chapter-number">11</span> 
<span class="chapter-title">Probability Theory, Part 2: Compound
Probability</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/probability_theory_3.html&lt;span-class='chapter-number'&gt;12&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Probability-Theory,-Part-3&lt;/span&gt;"><span class="chapter-number">12</span> 
<span class="chapter-title">Probability Theory, Part 3</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/probability_theory_4_finite.html&lt;span-class='chapter-number'&gt;13&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Probability-Theory,-Part-4:-Estimating-Probabilities-from-Finite-Universes&lt;/span&gt;"><span class="chapter-number">13</span> 
<span class="chapter-title">Probability Theory, Part 4: Estimating
Probabilities from Finite Universes</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/sampling_variability.html&lt;span-class='chapter-number'&gt;14&lt;/span&gt;--&lt;span-class='chapter-title'&gt;On-Variability-in-Sampling&lt;/span&gt;"><span class="chapter-number">14</span> 
<span class="chapter-title">On Variability in Sampling</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/monte_carlo.html&lt;span-class='chapter-number'&gt;15&lt;/span&gt;--&lt;span-class='chapter-title'&gt;The-Procedures-of-Monte-Carlo-Simulation-(and-Resampling)&lt;/span&gt;"><span class="chapter-number">15</span> 
<span class="chapter-title">The Procedures of Monte Carlo Simulation
(and Resampling)</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/standard_scores.html&lt;span-class='chapter-number'&gt;16&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Ranks,-Quantiles-and-Standard-Scores&lt;/span&gt;"><span class="chapter-number">16</span> 
<span class="chapter-title">Ranks, Quantiles and Standard
Scores</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/inference_ideas.html&lt;span-class='chapter-number'&gt;17&lt;/span&gt;--&lt;span-class='chapter-title'&gt;The-Basic-Ideas-in-Statistical-Inference&lt;/span&gt;"><span class="chapter-number">17</span> 
<span class="chapter-title">The Basic Ideas in Statistical
Inference</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/inference_intro.html&lt;span-class='chapter-number'&gt;18&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Introduction-to-Statistical-Inference&lt;/span&gt;"><span class="chapter-number">18</span> 
<span class="chapter-title">Introduction to Statistical
Inference</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/point_estimation.html&lt;span-class='chapter-number'&gt;19&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Point-Estimation&lt;/span&gt;"><span class="chapter-number">19</span> 
<span class="chapter-title">Point Estimation</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/framing_questions.html&lt;span-class='chapter-number'&gt;20&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Framing-Statistical-Questions&lt;/span&gt;"><span class="chapter-number">20</span> 
<span class="chapter-title">Framing Statistical Questions</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/testing_counts_1.html&lt;span-class='chapter-number'&gt;21&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Hypothesis-Testing-with-Counted-Data,-Part-1&lt;/span&gt;"><span class="chapter-number">21</span> 
<span class="chapter-title">Hypothesis-Testing with Counted Data, Part
1</span></span> <span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/significance.html&lt;span-class='chapter-number'&gt;22&lt;/span&gt;--&lt;span-class='chapter-title'&gt;The-Concept-of-Statistical-Significance-in-Testing-Hypotheses&lt;/span&gt;"><span class="chapter-number">22</span> 
<span class="chapter-title">The Concept of Statistical Significance in
Testing Hypotheses</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/testing_counts_2.html&lt;span-class='chapter-number'&gt;23&lt;/span&gt;--&lt;span-class='chapter-title'&gt;The-Statistics-of-Hypothesis-Testing-with-Counted-Data,-Part-2&lt;/span&gt;"><span class="chapter-number">23</span> 
<span class="chapter-title">The Statistics of Hypothesis-Testing with
Counted Data, Part 2</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/testing_measured.html&lt;span-class='chapter-number'&gt;24&lt;/span&gt;--&lt;span-class='chapter-title'&gt;The-Statistics-of-Hypothesis-Testing-With-Measured-Data&lt;/span&gt;"><span class="chapter-number">24</span> 
<span class="chapter-title">The Statistics of Hypothesis-Testing With
Measured Data</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/testing_procedures.html&lt;span-class='chapter-number'&gt;25&lt;/span&gt;--&lt;span-class='chapter-title'&gt;General-Procedures-for-Testing-Hypotheses&lt;/span&gt;"><span class="chapter-number">25</span> 
<span class="chapter-title">General Procedures for Testing
Hypotheses</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/confidence_1.html&lt;span-class='chapter-number'&gt;26&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Confidence-Intervals,-Part-1:-Assessing-the-Accuracy-of-Samples&lt;/span&gt;"><span class="chapter-number">26</span> 
<span class="chapter-title">Confidence Intervals, Part 1: Assessing the
Accuracy of Samples</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/confidence_2.html&lt;span-class='chapter-number'&gt;27&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Confidence-Intervals,-Part-2:-The-Two-Approaches-to-Estimating-Confidence-Intervals&lt;/span&gt;"><span class="chapter-number">27</span> 
<span class="chapter-title">Confidence Intervals, Part 2: The Two
Approaches to Estimating Confidence Intervals</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/reliability_average.html&lt;span-class='chapter-number'&gt;28&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Some-Last-Words-About-the-Reliability-of-Sample-Averages&lt;/span&gt;"><span class="chapter-number">28</span> 
<span class="chapter-title">Some Last Words About the Reliability of
Sample Averages</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/correlation_causation.html&lt;span-class='chapter-number'&gt;29&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Correlation-and-Causation&lt;/span&gt;"><span class="chapter-number">29</span> 
<span class="chapter-title">Correlation and Causation</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/how_big_sample.html&lt;span-class='chapter-number'&gt;30&lt;/span&gt;--&lt;span-class='chapter-title'&gt;How-Large-a-Sample?&lt;/span&gt;"><span class="chapter-number">30</span> 
<span class="chapter-title">How Large a Sample?</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/bayes_simulation.html&lt;span-class='chapter-number'&gt;31&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Bayesian-Analysis-by-Simulation&lt;/span&gt;"><span class="chapter-number">31</span> 
<span class="chapter-title">Bayesian Analysis by
Simulation</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/references.htmlReferences">References</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:quarto-sidebar-section-1">Appendices</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/exercise_solutions.html&lt;span-class='chapter-number'&gt;A&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Exercise-Solutions&lt;/span&gt;"><span class="chapter-number">A</span> 
<span class="chapter-title">Exercise Solutions</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/technical_note.html&lt;span-class='chapter-number'&gt;B&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Technical-Note-to-the-Professional-Reader&lt;/span&gt;"><span class="chapter-number">B</span> 
<span class="chapter-title">Technical Note to the Professional
Reader</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/acknowlegements.html&lt;span-class='chapter-number'&gt;C&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Acknowledgements&lt;/span&gt;"><span class="chapter-number">C</span> 
<span class="chapter-title">Acknowledgements</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/code_topics.html&lt;span-class='chapter-number'&gt;D&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Code-topics&lt;/span&gt;"><span class="chapter-number">D</span> 
<span class="chapter-title">Code topics</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/errors_suggestions.html&lt;span-class='chapter-number'&gt;E&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Errors-and-suggestions&lt;/span&gt;"><span class="chapter-number">E</span> 
<span class="chapter-title">Errors and suggestions</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-breadcrumbs-&lt;span-class='chapter-number'&gt;2&lt;/span&gt;--&lt;span-class='chapter-title'&gt;The-resampling-method&lt;/span&gt;"><span class="chapter-number">2</span> 
<span class="chapter-title">The resampling method</span></span>
</div>
<div class="hidden" id="quarto-meta-markdown">
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-metatitle"><span class="quarto-section-identifier" id="sec-resampling-method"><span class="chapter-number">2</span> 
<span class="chapter-title">The resampling method</span></span> –
Resampling statistics</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-twittercardtitle"><span class="quarto-section-identifier" id="sec-resampling-method"><span class="chapter-number">2</span> 
<span class="chapter-title">The resampling method</span></span> –
Resampling statistics</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-ogcardtitle"><span class="quarto-section-identifier" id="sec-resampling-method"><span class="chapter-number">2</span> 
<span class="chapter-title">The resampling method</span></span> –
Resampling statistics</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-metasitename">Resampling statistics</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-twittercarddesc"></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-ogcardddesc"></span>
</div>
