# Introducing data frames


Find this notebook on the web at Note .

R is a data analysis language, so, as you would expect, it is
particularly good at loading data files, and presenting them to us as a
useful table-like structure, called a *data frame*.

We start by using R to load our data file. R has a special function to
do this, called `read.csv`.

```{r}
district_income <- read.csv('data/congress_2023.csv')
```

We have thus far done many operations that returned R *vectors*.
`read.csv` returns a new type of value, called a *data frame*:

```{r}
class(district_income)
```

A data frame is R’s own way of representing a table, with columns and
rows. You can think of it as R’s version of a spreadsheet. Data frames
are a fundamental type in R, and there are many functions that operate
on them. Among them is the function `head` which selects (by default)
the first six rows of whatever you send it. Here we select the first six
rows of the data frame.

```{r}
# Show the first six rows in the data frame
head(district_income)
```

The data are in income order, sorted lowest to highest, so the first
five districts are those with the lowest household income.

We are particularly interested in the column named `Median_Income`.

You can fetch columns of data from a data frame by using R’s `$` syntax.
The `$` syntax means “fetch the thing named on the right of the `$`
attached to the value given to the left of the `$`”.

So, to get the data for the `Median_Income` column, we can write:

```{r}
# Use $ syntax to get a column of data from a data frame.
# "fetch the Median_Income thing from district_income".
incomes = district_income$Median_Income
# The thing that comes back is our familiar R vector.
# Show the first five values, by indexing with a slice.
incomes[1:5]
```
