# Simulating juries


Find this notebook on the web at
<a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/resampling_with_code2.html#nte-life_and_death">Note <span>6.1</span></a>.

### 6.3.2 Using code to simulate a trial

We use the same logic to simulate a trial with the computer. A little
code makes the job easier, because we can ask R to give us 12 random
numbers from 0 through 99, and to count how many of these numbers are in
the range from 75 through 99. Numbers in the range from 75 through 99
correspond to black jurors.

### 6.3.3 Random numbers from 0 through 99

We can now use R and `sample` from the last chapter to get 12 random
numbers from 0 through 99.

```{r}
# Get 12 random numbers from 0 through 99
a <- sample(0:99, size=12, replace=TRUE)

# Show the result
a
```

#### 6.3.3.1 Counting the jurors

We use *comparison* and `sum` to count how many numbers are greater than
74, and therefore, in the range from 75 through 99:

```{r}
# How many numbers are greater than 74?
b <- sum(a > 74)
# Show the result
b
```

#### 6.3.3.2 A single simulated trial

We assemble the pieces from the last few sections to make a chunk that
simulates a single trial:

```{r}
# Get 12 random numbers from 0 through 99
a <- sample(0:99, size=12, replace=TRUE)
# How many are greater than 74?
b <- sum(a > 74)
# Show the result
b
```

## 6.4 Three simulation steps

Now we come back to the details of how we:

1.  Repeat the simulated trial many times;
2.  record the results for each trial;
3.  calculate the required proportion as an estimate of the probability
    we seek.

Repeating the trial many times is the job of the `for` loop, and we will
come to that soon.

In order to record the results, we will store each trial result in a
vector.

### 6.4.1 More on vectors

Since we will be working with vectors a lot, it is worth knowing more
about them.

A vector is a *container* that stores many elements of the same type.
You have already seen, in
<a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/resampling_method.html"><span>Chapter 2</span></a>, how we
can create a vector from a sequence of numbers using the `c()` function.

```{r}
# Make a vector of numbers, store with the name "some_numbers".
some_numbers <- c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9)
# Show the value of "some_numbers"
some_numbers
```

Another way that we can create vectors is to use the `numeric` function
to make a new array where all the elements are 0.

```{r}
# Make a new vector containing 5 zeros.
z <- numeric(5)
# Show the value of "z"
z
```

Notice the argument `5` to the `numeric` function. This tells the
function how many zeros we want in the vector that the function will
return.

## 6.5 Vector length

The are various useful things we can do with this vector container. One
is to ask how many elements there are in the vector container. We can
use the `length` function to calculate the number of elements in a
vector:

```{r}
# Show the number of elements in "z"
length(z)
```

## 6.6 Indexing into vectors with integers

Another thing we can do with vectors is *set* the value for a particular
element. To do this, we use square brackets following the vector value,
on the left hand side of the equals sign, like this:

```{r}
# Set the value of the first element in the vector.
z[1] = 99
# Show the new contents of the vector.
z
```

Read the first line of code as “the element at position 1 gets a value
of 99”.

For practice, let us also set the value of the third element in the
vector:

```{r}
# Set the value of the third element in the vector.
z[3] <- 99
# Show the new contents of the vector.
z
```

Read the first code line above as as “set the value at position 3 in the
vector to have the value 99”.

We can also *get* the value of the element at a given position, using
the same square-bracket notation:

```{r}
# Get the value of the *first* element in the array.
# Store the value with name "v"
v = z[1]
# Show the value we got
v
```

Read the first code line here as “v gets the value at position 1 in the
vector”.

Using square brackets to get and set element values is called *indexing*
into the vector.

### 6.6.1 Repeating trials

As a preview, let us now imagine that we want to do 50 simulated trials
of Robert Swain’s jury in Hypothetical County. We will want to store the
count for each trial, to give 50 counts.

In order to do this, we make a vector to hold the 50 counts. Call this
vector `z`.

```{r}
# A vector to hold the 50 count values.
z <- numeric(50)
```

We could run a single trial to get a single simulated count. Here we
just repeat the code chunk you saw above. Notice that we can get a
different result each time we run this code, because the numbers in `a`
are *random* choices from the range 0 through 99, and different random
numbers will give different counts.

```{r}
# Get 12 random numbers from 0 through 99
a <- sample(0:99, size=12, replace=TRUE)
# How many are greater than 74?
b <- sum(a == 9)
# Show the result
b
```

Now we have the result of a single trial, we can store it as the first
number in the `z` vector:

```{r}
# Store the single trial count as the first value in the "z" vector.
z[1] <- b
# Show all the values in the "z" vector.
z
```

Of course we could just keep doing this: run the chunk corresponding to
a trial, above, to get a new count, and then store it at the next
position in the `z` vector. For example, we could store the counts for
the first three trials with:

```{r}
# First trial
a <- sample(0:99, size=12, replace=TRUE)
b <- sum(a == 9)
# Store the result at the first position in z
z[1] <- b

# Second trial
a <- sample(0:99, size=12, replace=TRUE)
b <- sum(a == 9)
# Store the result at the second position in z
z[2] <- b

# Third trial
a <- sample(0:99, size=12, replace=TRUE)
b <- sum(a == 9)
# Store the result at the third position in z
z[3] <- b

# And so on ...
```

This would get terribly long and boring to type for 50 trials. Luckily
computer code is very good at repeating the same procedure many times.
For example, R can do this using a `for` loop. You have already seen a
preview of the `for` loop in
<a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/resampling_method.html"><span>Chapter 2</span></a>. Here we
dive into `for` loops in more depth.

### 6.6.2 For-loops in R

A for-loop is a way of asking R to:

- Take a sequence of things, one by one, and
- Do the same task on each one.

We often use this idea when we are trying to explain a repeating
procedure. For example, imagine we wanted to explain what the
supermarket checkout person does for the items in your shopping basket.
You might say that they do this:

&gt; For each item of shopping in your basket, they take the item off the
&gt; conveyor belt, scan it, and put it on the other side of the till.

You could also break this description up into bullet points with
indentation, to say the same thing:

- For each item from your shopping basket, they:
  - Take the item off the conveyor belt.
  - Scan the item.
  - Put it on the other side of the till.

Notice the logic; the checkout person is repeating the same procedure
for each of a series of items.

This is the logic of the `for` loop in R. The procedure that R repeats
is called the *body of the for loop*. In the example of the checkout
person above, the repeating procedure is:

- Take the item off the conveyor belt.
- Scan the item.
- Put it on the other side of the till.

Now imagine we wanted to use R to print out the year of birth for each
of the authors for the third edition of this book:

| Author               | Year of birth |
|----------------------|---------------|
| Julian Lincoln Simon | 1932          |
| Matthew Brett        | 1964          |
| Stéfan van der Walt  | 1980          |

We want to see this output:

    Author birth year is 1932
    Author birth year is 1964
    Author birth year is 1980

Of course, we could just ask R to print out these exact lines, like
this:

```{r}
message('Author birth year is 1932')
```

```{r}
message('Author birth year is 1964')
```

```{r}
message('Author birth year is 1980')
```

We might instead notice that we are repeating the same procedure for
each of the three birth years, and decide to do the same thing using a
`for` loop:

```{r}
author_birth_years <- c(1932, 1964, 1980)

# For each birth year
for (birth_year in author_birth_years) {
    # Repeat this procedure ...
    message('Author birth year is ', birth_year)
}
```

The `for` loop starts with a line where we tell it what items we want to
repeat the procedure for:

    for (birth_year in author_birth_years) {

This *initial line* of the `for` loop ends with an *opening curly brace*
`{`. The opening curly brace tells R that what follows, up until the
matching closing curly brace `}`, is the procedure R should follow for
each item. The lines between the opening `{` and closing `}` curly
braces\* are the *body of the for loop*.

The initial line of the `for` loop above tells R that it should take
*each item* in `author_birth_years`, one by one — first 1932, then 1964,
then 1980. For each of these numbers it will:

- Put the number into the variable `birth_year`, then
- Run the code between the curly braces.

Just as the person at the supermarket checkout takes each item in turn,
for each iteration (repeat) of the `for` loop, `birth_year` gets a new
value from the sequence in `author_birth_years`. `birth_year` is called
the *loop variable*, because it is the variable that gets a new value
each time we begin a new iteration of the `for` loop procedure. As for
any variable in R, we can call our loop variable anything we like. We
used `birth_year` here, but we could have used `y` or `year` or some
other name.

Notice that R insists we put parentheses (round brackets) around: the
loop variable; `in`; and the sequence that will fill the loop variable —
like this:

    for (birth_year in author_birth_years) {

Do not forget these round brackets — R insists on them.

Now you know what the `for` loop is doing, you can see that the `for`
loop above is equivalent to the following code:

```{r}
birth_year <- 1932  # Set the loop variable to contain the first value.
message('Author birth year is ', birth_year)  # Use the first value.
```

```{r}
birth_year <- 1964  # Set the loop variable to contain the next value.
message('Author birth year is ', birth_year)  # Use the second value.
```

```{r}
birth_year <- 1980
message('Author birth year is ', birth_year)
```

Writing the steps in the `for` loop out like this is called *unrolling*
the loop. It can be a useful exercise to do this when you come across a
`for` loop, in order to work through the logic of the loop. For example,
you may want to write out the unrolled equivalent of the first couple of
iterations, to see what the loop variable will be, and what will happen
in the body of the loop.

We often use `for` loops with ranges (see
<a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/resampling_with_code.html#sec-ranges"><span>Section 5.9</span></a>). Here we use a loop
to print out the numbers 1 through 4:

```{r}
for (n in 1:4) {
    message('The loop variable n is ', n)
}
```

Notice that the range ended at 4, and that means we repeat the loop body
4 times. We can also use the loop variable value from the range as an
*index*, to get or set the first, second, etc values from a vector.

For example, maybe we would like to show the author position *and* the
author year of birth.

Remember our author birth years:

```{r}
author_birth_years
```

We can get (for example) the second author birth year with:

```{r}
author_birth_years[2]
```

Using the combination of looping over a range, and vector indexing, we
can print out the author position *and* the author birth year:

```{r}
for (n in 1:3) {
    year <- author_birth_years[n]
    message('Birth year of author position ', n, ' is ', year)
}
```

Just for practice, let us unroll the three iterations through this `for`
loop, to remind ourselves what the code is doing:

```{r}
# Unrolling the for loop.
n <- 1
year <- author_birth_years[n]  # Will be 1932
message('Birth year of author position ', n, ' is ', year)
```

```{r}
n <- 2
year <- author_birth_years[n]  # Will be 1964
message('Birth year of author position ', n, ' is ', year)
```

```{r}
n <- 3
year <- author_birth_years[n]  # Will be 1980
message('Birth year of author position ', n, ' is ', year)
```

### 6.6.3 Putting it all together

Here is the code we worked out above, to implement a single trial:

```{r}
# Get 12 random numbers from 0 through 99
a <- sample(0:99, size=12, replace=TRUE)
# How many are greater than 74?
b <- sum(a == 9)
# Show the result
b
```

We found that we could use vectors to store the results of these trials,
and that we could use `for` loops to repeat the same procedure many
times.

Now we can put these parts together to do 50 simulated trials:

```{r}
# Procedure for 50 simulated trials.

# A vector to store the counts for each trial.
z <- numeric(50)

# Repeat the trial procedure 50 times.
for (i in 1:50) {
    # Get 12 random numbers from 0 through 99
    a <- sample(0:99, size=12, replace=TRUE)
    # How many are greater than 74?
    b <- sum(a > 74)
    # Store the result at the next position in the "z" vector.
    z[i] = b
    # Now go back and do the next trial until finished.
}
# Show the result of all 50 trials.
z
```

Finally, we need to count how many of the trials in `z` ended up with
all-white juries. These are the trials with a `z` (count) value of 0.

To do this, we can ask a vector which elements match a certain
condition. E.g.:

```{r}
x <- c(2, 1, 3, 0)
y = x < 2
# Show the result
y
```

We now use that same technique to ask, of *each of the 50 counts*,
whether the vector `z` is equal to 0, like this:

```{r}
# Is the value of z equal to 0?
all_white <- z == 0
# Show the result of the comparison.
all_white
```

We need to get the number of `TRUE` values in `all_white`, to find how
many simulated trials gave all-white juries.

```{r}
# Count the number of True values in "all_white"
# This is the same as the number of values in "z" that are equal to 0.
n_all_white = sum(all_white)
# Show the result of the comparison.
n_all_white
```

`n_all_white` is the number of simulated trials for which all the jury
members were white. It only remains to get the proportion of trials for
which this was true, and to do this, we divide by the number of trials.

```{r}
# Proportion of trials where all jury members were white.
p <- n_all_white / 50
# Show the result
p
```

From this initial simulation, it seems there is around a 4% chance that
a jury selected randomly from the population, which was 26% black, would
have no black jurors.

## 6.7 Many many trials

Our experiment above is only 50 simulated trials. The higher the number
of trials, the more confident we can be of our estimate for `p` — the
proportion of trials where we get an all-white jury.

It is no extra trouble for us to tell the computer to do a very large
number of trials. For example, we might want to run 10,000 trials
instead of 50. All we have to do is to run the loop 10,000 times instead
of 50 times. The computer has to do more work, but it is more than up to
the job.

Here is exactly the same code we ran above, but collected into one
chunk, and using 10,000 trials instead of 50. We have left out the
comments, to make the code more compact.

```{r}
# Full simulation procedure, with 10,000 trials.
z <- numeric(10000)
for (i in 1:10000) {
    a <- sample(0:99, size=12, replace=TRUE)
    b <- sum(a > 74)
    z[i] = b
}
all_white <- z == 0
n_all_white <- sum(all_white)
p <- n_all_white / 10000
p
```

We now have a new, more accurate estimate of the proportion of
Hypothetical County juries that are all white. The proportion is 0.032,
and so 3.2%.

This proportion means that, for any one jury from Hypothetical County,
there is a less than one in 20 chance that the jury would be all white.

As we will see in more detail later, we might consider using the results
from this experiment in Hypothetical County, to reflect on the result we
saw in the real Talladega County. We might conclude, for example, that
there was likely some systematic difference between Hypothetical County
and Talledega County. Maybe the difference was that there was, in fact,
some bias in the jury selection in Talledega county, and that the
Supreme Court was wrong to reject this. You will hear more of this line
of reasoning later in the book.

