# Simulating lymphoma trials


Find this notebook on the web at
<a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/resampling_with_code.html#nte-lymphoma">Note <span>5.1</span></a>.

## 5.5 Simulate one trial with code

We can use the computer to do something very similar to rolling 17
10-sided dice, by asking the computer for 17 random whole numbers from 0
through 9.

**Note: Whole numbers**

A whole number is a number that is not negative, and does not have
fractional part (does not have anything after a decimal point). 0 and 1
and 2 and 3 are whole numbers, but -1 and $\frac{3}{5}$ and 11.3 are
not. The whole numbers from 0 through 9 are 0, 1, 2, 3, 4, 5, 6, 7, 8,
9.

**End of Note: Whole numbers**

We have already discussed what we mean by *random* in
<a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/resampling_method.html#sec-randomness-computer"><span>Section 2.2</span></a>.

## 5.6 From numbers to vectors

We need to prepare the *sequence* of numbers that we want R to select
from.

We have already seen the idea that R has *values* that are individual
numbers. Remember, a *variable* is a *named value*. Here we attach the
name `a` to the value 1.

```{r}
a <- 1
# Show the value of "a"
a
```

R also allows *values* that are *sequences of numbers*. R calls these
sequences *vectors*.

The name *vector* sounds rather technical and mathematical, but the only
important idea for us is that a *vector* stores a *sequence* of numbers.

Here we make a vector that contains the 10 numbers we will select from:

```{r}
# Make a vector of numbers, store with the name "some_numbers".
some_numbers <- c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9)
# Show the value of "some_numbers"
some_numbers
```

Notice that the value for `some_numbers` is a vector, and that this
value *contains* 10 numbers.

Put another way, `some_numbers` is now the name we can use for this
collection of 10 values.

Vectors are very useful for simulations and data analysis, and we will
be using them for nearly every example in this book.

## 5.7 Functions

*Functions* are another tool that we will be using everywhere, and that
you seen already, although we have not introduced them until now.

You can think of functions as named *production lines*.

For example, consider the R *function* `round`

`round` is the name for a simple production line, that takes in a
number, and (by default) sends back the number rounded to the nearest
*integer*.

**Note: What is an integer?**

An *integer* is a positive or negative *whole number*.

In other words, a number is an *integer* if the number is *either* a
whole number (0, 1, 2 …), *or* a negative whole number (-1, -2, -3 …).
All of -208, -2, 0, 10, 105 are integers, but $\frac{3}{5}$, -10.3 and
0.2 are not.

We will use the term *integer* fairly often, because it is a convenient
way to name all the positive and negative whole numbers.

**End of Note: What is an integer?**

Think of a function as a named *production line*. We sent the function
(production line) raw material (components) to work on. The production
line does some work on the components. A finished result comes off the
other end.

Therefore, think of `round` as the name of a production line, that takes
in a *component* (in this case, any number), and does some work, and
sends back the finished *result* (in this case, the number rounded to
the nearest integer.

The components we send to a function are called *arguments*. The
finished result the function sends back is the *return value*.

- **Arguments**: the value or values we send to a function. These are
  the components in the production line analogy.
- **Return value**: the values the function sends back. This is the
  finished result in the production line analogy.

See <a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/resampling_with_code.html#fig-round_function_pl">Figure <span>5.2</span></a> for an
illustration of `round` as a production line.

In the next few code chunks, you see examples where `round` takes in a
not-integer number, as an *argument*, and sends back the nearest integer
as the *return value*:

```{r}
# Put in 3.2, round sends back 3.
round(3.2)
```

```{r}
# Put in -2.7, round sends back -3.
round(-2.7)
```

Like many functions, `round` can take more than one argument
(component). You can send `round` the number of digits you want to round
to, after the number of you want it to work on, like this (see
<a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/resampling_with_code.html#fig-round_ndigits_pl">Figure <span>5.3</span></a>):

```{r}
# Put in 3.1415, and the number of digits to round to (2).
# round sends back 3.14
round(3.1415, 2)
```

Notice that the second argument — here 2 — is *optional*. We only have
to send `round` one argument: the number we want it to round. But we can
*optionally* send it a second argument — the number of decimal places we
want it to round to. If we don’t specify the second argument, then
`round` assumes we want to round to 0 decimal places, and therefore, to
the nearest integer.

## 5.8 Functions and named arguments

In the example above, we sent `round` two arguments. `round` knows that
we mean the first argument to be the number we want to round, and the
second argument is the number of decimal places we want to round to. It
knows which is which by the *position* of the arguments — the *first*
argument is the *number* it should round, and *second* is the number of
digits.

In fact, internally, the `round` function also gives these arguments
*names*. It calls the number it should round — `x` — and the number of
digits it should round to — `digits`. This is useful, because it is
often clearer and simpler to identify the argument we are specifying
with its name, instead of just relying on its position.

If we aren’t using the argument names, we call the round function as we
did above:

```{r}
# Put in 3.1415, and the number of digits to round to (2).
# round sends back 3.14
round(3.1415, 2)
```

In this call, we relied on the fact that we, the people writing the
code, and you, the person reading the code, remembered that the second
argument (2) means the number of decimal places it should round to. But
we can also specify the argument using its name, like this (see
<a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/resampling_with_code.html#fig-round_function_named">Figure <span>5.4</span></a>):

```{r}
# Put in 3.1415, and the number of digits to round to (2).
# Use the name of the number-of-decimals argument for clarity:
round(3.1415, digits=2)
```

Here R sees the *first* argument, as before, and assumes that it is the
number we want to round. Then it sees the second, named argument —
`digits=2` — and knows, *from the name*, that we mean this to be the
number of decimals to round to.

In fact, we could even specify *both* arguments by name, like this:

```{r}
# Put in 3.1415, and the number of digits to round to (2).
# Name both arguments.
round(x=3.1415, digits=2)
```

We don’t usually name both arguments for `round`, as we have above,
because it is so obvious that the first argument is the thing we want to
round, and so naming the argument does not make it any more clear what
the code is doing. But — as so often in programming — whether to use the
names, or let R work out which argument is which by position, is a
judgment call. The judgment you are making is about the way to write the
code to be most clear for your reader, where your most important reader
may be you, coming back to the code in a week or a year.

**Note: How do you know what names to use for the function arguments?**

You can find the names of the function arguments in the help for the
function, either online, or in the notebook interface. For example, to
get the help for `round`, including the argument names, you could make a
new chunk, and type `?round`, then execute the cell by running the
chunk. This will show the help for the function in the notebook
interface.

**End of Note: How do you know what names to use for the function
arguments?**

## 5.9 Ranges

Now let us return to the variable `some_numbers` that we created above:

```{r}
# Make a vector of numbers, store with the name "some_numbers".
some_numbers <- c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9)
# Show the value of "some_numbers"
some_numbers
```

In fact, we often need to do this: generate a sequence or *range* of
integers, such as 0 through 9.

**Note: Pick a number from 1 through 5**

Ranges can be confusing in normal speech because it is not always clear
whether they include their beginning and end. For example, if someone
says “pick a number between 1 and 5”, do they mean to pick from *all* of
the numbers, including the first and last (any of 1 or 2 or 3 or 4 or
5)? Or do they mean only the numbers that are *between* 1 and 5 (so 2 or
3 or 4)? Or do they mean all the numbers up to, but not including 5 (so
1 or 2 or 3 or 4)?

To avoid this confusion, we will nearly always use “from” and “through”
in ranges, meaning that we do include both the start and the end number.
For example, if we say “pick a number from 1 through 5” we mean one of 1
or 2 or 3 or 4 or 5.

**End of Note: Pick a number from 1 through 5**

Creating ranges of numbers is so common that R has a special syntax to
do that.



R allows you to write a colon (`:`) between two values, to mean that you
want a *vector* (sequence) that is all the integers from the first value
(before the colon) *through* the second value (after the colon):

```{r}
# A vector containing all the integers from 0 through 9.
some_integers = 0:9
some_integers
```

Here are some more examples of the colon syntax:

```{r}
# All the integers from 10 through 14
10:14
```

```{r}
# All the integers from -1 through 5
-1:5
```

## 5.10 Choosing values at random

We can use the `sample` function to select a single value *at random*
from the sequence of numbers in `some_integers`.

**Note: More on sample**

The `sample` function will be a fundamental tool for taking many kinds
of samples, and we cover it in more detail in
<a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/sampling_tools.html"><span>Chapter 7</span></a>.

**End of Note: More on sample**

```{r}
# Select 1 integer (the second argument) from the choices in some_integers
# (the first argument).
my_integer <- sample(some_integers, 1)
# Show the value that results.
my_integer
```

Like `round` (above), `sample` is a *function*.

As you remember, a function is a named *production line*. In our case,
the production line has the name the `sample` function.

We sent the `sample` function. a value to work on — an *argument*. In
this case, the argument was the value of `some_integers`.

`sample` also needs the number of random values we should select from
the first argument. We can send the number of values we want with the
*second argument*.

<a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/resampling_with_code.html#fig-sample_pl">Figure <span>5.5</span></a> is a diagram
illustrating an example run of the `sample` function (production line).

Here is the same code again, with new comments.

```{r}
# Send the value of "some_integers" to sample.
# some_integers is the *argument*.  Ask sample to return 1 of the values.
# Put the *return* value from the function into "my_number".
my_number <- sample(some_integers, 1)
# Show the value that results.
my_number
```

## 5.11 Creating vectors with sampling

In the code above, we asked R to select a single number at random — by
sending 1 as the second argument to the function.

As you can imagine, we can tell `sample` to select *any number of
values* at random, by changing the second argument to the function.

In our case, we would like R to select 17 numbers at random from the
sequence of `some_integers`.

But — there is a complication here. By default, `sample` selects numbers
from the first argument *without replacement*, meaning that, by default,
sample cannot select the same number twice, and in our case, where we
want 17 numbers, that is bad, because `sample` is going to run out of
numbers. To get the result we want, we must also add an extra argument:
`replace=TRUE`. `replace=TRUE` tells R to sample `some_integers` *with
replacement*, where `sample` can select the same number more than once
in the same sample. Sampling with and without replacement is a
fundamental distinction in probability and statistics.
<a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/sampling_tools.html"><span>Chapter 7</span></a> goes into
much more detail about this, but for now, please take our word for it
that using `replace=TRUE` for `sample` gives us the same effect as
rolling several 10-sided dice.

```{r}
# Get 17 values from the *some_integers* vector.
# Sample *with replacement*, so sample can select numbers more than once.
# Store the 17 numbers with the name "a"
a <- sample(some_integers, 17, replace=TRUE)
# Show the result.
a
```

As you can see, the function sent back (returned) 17 numbers. Because it
is sending back more than one number, the thing it sends back is a
vector, where the vector has 17 elements.

### 5.11.1 `sum` — adding all the values

Bear with us for a short diversion. You will see why we made this
diversion soon.

R has a function `sum` that will add up all the numbers in a vector.

You can see the contents of `a` above.

`sum` adds all the numbers in the vector together, to give the *sum* of
the vector. The *sum* is just the result of adding all the values in the
vector. Put another way, it is the result of adding the second element
to the first, then adding third element to the result, and the fourth
element to the result, and so on.

```{r}
sum(a)
```

## 5.12 Counting results

We now have the code to do the equivalent of throwing 17 ten-sided dice.
This is the basis for one simulated trial in the world of Saint
Hypothetical General.

Our next job is to get the code to count the number of numbers that are
not zero in the vector `a`. That will give us the number of patients who
were cured in simulated trial.

Another way of asking this question, is to ask how many elements in `a`
are greater than zero.

### 5.12.1 Comparison

To ask whether a number is greater than zero, we use *comparison*. Here
is a *greater than zero* comparison on a single number:

```{r}
n <- 5
# Is the value of n greater than 0?
# Show the result of the comparison.
n > 0
```

`&gt;` is a *comparison* — it *asks a question* about the numbers either
side of it. In this case `&gt;` is asking the question “is the value of `n`
(on the left hand side) greater than 0 (on the right hand side)?” The
value of `n` is 5, so the question becomes, “is 5 greater than 0?” The
answer is Yes, and R represents this Yes answer as the value `TRUE`.

In contrast, the comparison below boils down to “is 0 greater than 0?”,
to which the answer is No, and R represents this as `FALSE`.

```{r}
p <- 0
# Is the value of p greater than 0?
# Show the result of the comparison.
p > 0
```

So far you have seen the results of comparison on a single number. Now
say we do the same comparison on a vector. For example, say we ask the
question “is the value of `a` greater than 0”? Remember, `a` is a vector
containing 17 values. We are comparing 17 values to one value (0). What
answer do you think R will give? You may want to think a little about
this before you read on.

As a reminder, here is the current value for `a`:

```{r}
# Show the current value for "a"
a
```

Now you have had some time to think, here is what happens:

```{r}
# Is the value of "a" greater than 0?
# Show the result of the comparison.
a > 0
```

There are 17 values in `a`, so the comparison to 0 means there are 17
comparisons, and 17 answers. R therefore returns *a vector* of 17
elements, containing these 17 answers. The first answer is the answer to
the question “is the value of the *first* element of `a` greater than
0”, and the second is the answer to “is the value of the *second*
element of `a` greater than 0”.

Let us store the result of this comparison to work on:

```{r}
# Is the value of "a" greater than 0?
# Store as another vector "q".
q <- a > 0
# Show the value of q
q
```

## 5.13 Counting `TRUE` values with `sum`

Notice above that there is one `TRUE` element in `q` for every element
in `a` that was greater than 0. It only remains to *count* the number of
`TRUE` values in `q`, to get the count of patients in our simulated
trial who were cured.

We can use the R function `sum` to count the number of `TRUE` elements
in a vector. As you can see above, `sum` adds up all the elements in a
vector, to give a single number. This will work as we want for the `q`
vector, because R counts `FALSE` as equal to 0 and `TRUE` as equal to 1:

```{r}
# Question: is FALSE equal to 0?
# Answer - Yes! (TRUE)
FALSE == 0
```

```{r}
# Question: is TRUE equal to 1?
# Answer - Yes! (TRUE)
TRUE == 1
```

Therefore, the function `sum`, when applied to a vector of `TRUE` and
`FALSE` values, will count the number of `TRUE` values in the vector.

To see this in action we can make a new vector of `TRUE` and `FALSE`
values, and try using `sum` on the new array.

```{r}
# A vector containing three TRUE values and two FALSE values.
trues_and_falses <- c(TRUE, FALSE, TRUE, TRUE, FALSE)
# Show the new vector.
trues_and_falses
```

The `sum` operation adds all the elements in the vector. Because `TRUE`
counts as 1, and `FALSE` counts as 0, adding all the elements in
`trues_and_falses` is the same as adding up the values 1 + 0 + 1 + 1 +
0, to give 3.

We can apply the same operation on `q` to count the number of `TRUE`
values.

```{r}
# Count the number of TRUE values in "q"
# This is the same as the number of values in "a" that are greater than 0.
b <- sum(q)
# Show the result
b
```

## 5.14 The procedure for one simulated trial

We now have the whole procedure for one simulated trial. We can put the
whole procedure in one chunk:

```{r}
# Procedure for one simulated trial

# Get 17 values from the *some_integers* vector.
# Store the 17 numbers with the name "a"
a <- sample(some_integers, 17, replace=TRUE)
# Is the value of "a" greater than 0?
q <- a > 0
# Count the number of TRUE values in "q"
b <- sum(q)
# Show the result of this simulated trial.
b
```

## 5.15 Repeating the trial

Now we know how to do one simulated trial, we could just keep running
the chunk above, and writing down the result each time. Once we had run
the chunk 100 times, we would have 100 counts. Then we could look at the
100 counts to see how many were equal to 17 (all 17 simulated patients
cured on that trial). At least that would be much faster than rolling 17
dice 100 times, but we would also like the computer to automate the
process of repeating the trial, and keeping track of the counts.

Please forgive us as we race ahead again, as we did in the last chapter.
As in the last chapter, we will use a *results* vector called `z` to
store the count for each trial. As in the last chapter, we will use a
`for` loop to repeat the trial procedure many times. As in the last
chapter, we will not explain the counts vector of the `for` loop in any
detail, because we are going to cover those in the next chapter.

Let us now imagine that we want to do 100 simulated trials at Saint
Hypothetical General. This will give us 100 counts. We will want to
store the count for each trial.

To do this, we make a vector called `z` to hold the 100 counts. We have
called the vector `z`, but we could have called it anything we liked,
such as `counts` or `results` or `cecilia`.

```{r}
# A vector to hold the 100 count values.
# Later, we will fill this in with real count values from simulated trials.
z <- numeric(100)
```

Next we use a `for` loop to *repeat the single trial procedure*.

Notice that the single trial procedure, inside this `for` loop, is the
same as the single trial procedure above — the only two differences are:

- The trial procedure is inside the loop, and
- We are storing the count for each trial as we go.

We will go into more detail on how this works in the next chapter.

```{r}
# Procedure for 100 simulated trials.

# A vector to store the counts for each trial.
z <- numeric(100)

# Repeat the trial procedure 100 times.
for (i in 1:100) {
    # Get 17 values from the *some_integers* vector.
    # Store the 17 numbers with the name "a"
    a <- sample(some_integers, 17, replace=TRUE)
    # Is the value of "a" greater than 0?
    q <- a > 0
    # Count the number of TRUE values in "q".
    b <- sum(q)
    # Store the result at the next position in the "z" vector.
    z[i] = b
    # Now go back and do the next trial until finished.
}
# Show the result of all 100 trials.
z
```

Finally, we need to count how many of the trials results we stored in
`z` gave a “cured” count of 17.

We can ask the question whether a single number is equal to 17 using the
*double equals* comparison: `==`.

```{r}
s <- 17
# Is the value of s equal to 17?
# Show the result of the comparison.
s == 17
```

**Note**

<div class="Python">

## 5.16 Single and double equals

Notice that the *double equals* `==` means something entirely different
to Python than the single equals `=`. In the code above, Python reads
`s = 17` to mean “Set the variable `s` to have the value 17”. In
technical terms the single equals is called an *assignment* operator,
because it means *assign* the value 17 to the variable `s`.

The code `s == 17` has a completely different meaning.

</div>

## 5.17 Double equals

The *double equals* `==` above is a *comparison* in R.

It means “give `TRUE` if the value in `s` is equal to 17, and `FALSE`
otherwise”. The `==` is a *comparison* operator — it is for comparing
two values — here the value in `s` and the value 17. This comparison,
like all comparisons, returns an answer that is either `TRUE` or
`FALSE`. In our case `s` has the value 17, so the comparison becomes
`17 == 17`, meaning “is 17 equal to 17?”, to which the answer is “Yes”,
and R sends back `TRUE`.

**End of Note**

We can ask this question of *all 100 counts* by asking the question: is
the vector `z` equal to 17, like this:

```{r}
# Is the value of z equal to 17?
were_cured <- z == 17
# Show the result of the comparison.
were_cured
```

Finally we use `sum` to count the number of `TRUE` values in the
`were_cured` vector, to give the number of trials where all 17 patients
were cured.

```{r}
# Count the number of TRUE values in "were_cured"
# This is the same as the number of values in "z" that are equal to 17.
n_all_cured <- sum(were_cured)
# Show the result of the comparison.
n_all_cured
```

`n_all_cured` is the number of simulated trials for which all patients
were cured. It only remains to get the proportion of trials for which
this was true, and to do this, we divide by the number of trials.

```{r}
# Proportion of trials where all patients were cured.
p <- n_all_cured / 100
# Show the result
p
```

From this experiment, we see that there is roughly a one-in-six chance
that all 17 patients are cured when using a 90% effective treatment.

