# Sampling tools


Find this notebook on the web at
<a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/sampling_tools.html#nte-sampling_tools">Note <span>7.1</span></a>.

## 7.2 Samples and labels and strings

Thus far we have used numbers such as 1 and 0 and 10 to represent the
elements we are sampling from. For example, in
<a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/resampling_with_code2.html"><span>Chapter 6</span></a>, we were
simulating the chance of a particular juror being black, given that 26%
of the eligible jurors in the county were black. We used *integers* for
that task, where we started with all the integers from 0 through 99, and
asked R to select values at random from those integers. When R selected
an integer from 0 through 25, we chose to label the resulting simulated
juror as black — there are 26 integers in the range 0 through 25, so
there is a 26% chance that any one integer will be in that range. If the
integer was from 26 through 99, the simulated juror was white (there are
74 integers in the range 26 through 99).

Here is the process of simulating a single juror, adapted from
<a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/resampling_with_code2.html#sec-random-zero-through-ninety-nine"><span>Section 6.3.3</span></a>:

```{r}
# Get 1 random number from 0 through 99
# replace=TRUE is redundant here (why?), but we leave it for consistency.
a <- sample(0:99, 1, replace=TRUE)

# Show the result
a
```

After that, we have to unpack our labeling of 0 through 25 as being
“black” and 26 through 99 as being “white”. We might do that like this:

```{r}
this_juror_is_black <- a < 26
this_juror_is_black
```

This all works as we want it to, but it’s just a little bit difficult to
remember the coding (less than 26 means “black”, greater than 25 means
“white”). We had to use that coding because we committed ourselves to
using random numbers to simulate the outcomes.

However, R can also store bits of text, called *strings*. Values that
are bits of text can be very useful because the text values can be
memorable labels for the entities we are sampling from, in our
simulations.

Before we get to strings, let us consider the type of the values we have
seen so far.

## 7.3 Types of values in R



So far, all the values we have seen in R are *numeric* — integers or
floating point values. This is an integer value:

```{r}
v <- 10
v
```

Here the variable `v` holds the value. We can see what type of value `v`
holds by using the `class` function:

```{r}
class(v)
```

The value contained by the variable `v` is of `'numeric'` type (class).
This is the type of value that can store both integer values (positive
or negative whole numbers), or floating point values (values that can
have digits after a decimal point. Here’s a floating point value.

```{r}
f <- 10.1
class(f)
```

Notice that R also see this as a `"numeric"` type of value. However, we
are about to see that R values can be of other types, that are not
numeric.



## 7.4 String values

So far, all the values you have seen in R vectors have been numbers. Now
we get on to values that are bits of text. These are called *strings*.

Here is a single R string value:

```{r}
s <- "Resampling"
s
```

What is the `class` of the new bit-of-text value `s`?

```{r}
class(s)
```

The R `character` value is a bit of text, and therefore consists of a
sequence of characters.

As vectors are containers for other things, such as numbers, strings are
containers for characters.

To get the length of a string, use the `nchar` function (Number of
Characters):

```{r}
# Number of characters in s
nchar(s)
```

R has a `substring` function that allows you to select individual
characters or sequences of characters from a string. The arguments to
`substring` are: first — the string; second — the index of the first
character you want to select; and third — the index of the last
character you want to select. For example to select the second character
in the string you would specify 2 as the starting index, and 2 as the
ending index, like this:

```{r}
# Get the second character of the string
second_char <- substring(s, 2, 2)
second_char
```

## 7.5 Strings in vectors

As we can store numbers as elements in vectors, we can also store
strings as vector elements.

```{r}
vector_of_strings = c('Julian', 'Lincoln', 'Simon')
vector_of_strings
```



As for any vector, you can select elements with *indexing*. When you
select an element with a given position (index), you get the *string* at
at that position:

Notice the output from this chunk:

```{r}
# Julian Lincoln Simon's second name
middle_name <- vector_of_strings[2]
middle_name
```

As for numbers, we can compare strings with, for example, the `==`
operator, that asks whether the two strings are equal:

```{r}
middle_name == 'Lincoln'
```

## 7.6 Repeating elements

Now let us go back to the problem of selecting black and white jurors.

We started with the strategy of using numbers 0 through 25 to mean
“black” jurors, and 26 through 99 to mean “white” jurors. We selected
values at random from 0 through 99, and then worked out whether the
number meant a “black” juror (was less than 26) or a “white” juror (was
greater than 25).

It would be good to use strings instead of numbers to identify the
potential jurors. Then we would not have to remember our coding of 0
through 25 and 26 through 99.

If only there was a way to make a vector of 100 strings, where 26 of the
strings were “black” and 74 were “white”. Then we could select randomly
from that array, and it would be immediately obvious that we had a
“black” or “white” juror.

Luckily we can do that, by using the `rep` function to construct the
vector.

**Note: With or without replacement for the original jury selection**

You may have noticed in
<a class="quarto-xref" href="https://resampling-stats.github.io/latest-r/resampling_with_code2.html"><span>Chapter 6</span></a> that we were
sampling Robert Swain’s jury from the eligible pool of jurors, *with
replacement*. You might reasonably ask whether we should have selected
from the eligible jurors *without replacement*, given that the same
juror cannot serve more than once in the same jury, and therefore, the
same argument applies there as here.

The trick there was that we were selecting from a very large pool of
many thousand eligible jurors, of whom 26% were black. Let’s say there
were 10,000 eligible jurors, of whom 2,600 were black. When selecting
the first juror, there is exactly a 2,600 in 10,000 chance of getting a
black juror — 26%. If we do get a black juror first, then the chance
that the second juror will be black has changed slightly, 2,599 in
9,999. But these changes are very small; even if we select eleven black
jurors out of eleven, when we come to the twelfth juror, we still have a
2,589 out of 9,989 chance of getting another black juror, and that works
out at a 25.92% chance — hardly changed from the original 26%. So yes,
you’d be right, we really should have compiled our population of 2,600
black jurors and 7,400 white jurors, and then sampled without
replacement from that population, but as the resulting sample
probabilities will be very similar to the simpler sampling with
replacement, we chose to try and slide that one quietly past you, in the
hope you would forgive us when you realized.

**End of Note: With or without replacement for the original jury
selection**

## 7.7 Conclusion

This chapter introduced you to the idea of strings — values in R that
store bits of text. Strings are very useful as labels for the entities
we are sampling from, when we do our simulations. Strings are
particularly useful when we use them with vectors, and one way we often
do that is to build up vectors of strings to sample from, using the
`rep` function.

There is a fundamental distinction between two different types of
sampling — sampling *with replacement*, where we draw an element from a
larger pool, then put that element back before drawing again, and
sampling *without replacement*, where we remove the element from the
remaining pool when we draw it into the sample. As we will see later, it
is often a judgment call which of these two types of sampling is a more
reasonable model of the world you are trying to simulate.

<div class="hidden" id="quarto-navigation-envelope">
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar-title">Resampling statistics</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-navbar-title">Resampling statistics</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-next"><span class="chapter-number">8</span> 
<span class="chapter-title">Probability Theory, Part 1</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-prev"><span class="chapter-number">6</span> 
<span class="chapter-title">More resampling with code</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/index.html{{&lt;-var-lang-&gt;}}-version">R
version</span> <span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/preface_third.htmlPreface-to-the-third-edition">Preface
to the third edition</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/preface_second.htmlPreface-to-the-second-edition">Preface
to the second edition</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/intro.html&lt;span-class='chapter-number'&gt;1&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Introduction&lt;/span&gt;"><span class="chapter-number">1</span> 
<span class="chapter-title">Introduction</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/resampling_method.html&lt;span-class='chapter-number'&gt;2&lt;/span&gt;--&lt;span-class='chapter-title'&gt;The-resampling-method&lt;/span&gt;"><span class="chapter-number">2</span> 
<span class="chapter-title">The resampling method</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/what_is_probability.html&lt;span-class='chapter-number'&gt;3&lt;/span&gt;--&lt;span-class='chapter-title'&gt;What-is-probability?&lt;/span&gt;"><span class="chapter-number">3</span> 
<span class="chapter-title">What is probability?</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/about_technology.html&lt;span-class='chapter-number'&gt;4&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Introducing-{{&lt;-var-lang-&gt;}}-and-the-Jupyter-notebook&lt;/span&gt;"><span class="chapter-number">4</span> 
<span class="chapter-title">Introducing R and the Jupyter
notebook</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/resampling_with_code.html&lt;span-class='chapter-number'&gt;5&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Resampling-with-code&lt;/span&gt;"><span class="chapter-number">5</span> 
<span class="chapter-title">Resampling with code</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/resampling_with_code2.html&lt;span-class='chapter-number'&gt;6&lt;/span&gt;--&lt;span-class='chapter-title'&gt;More-resampling-with-code&lt;/span&gt;"><span class="chapter-number">6</span> 
<span class="chapter-title">More resampling with code</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/sampling_tools.html&lt;span-class='chapter-number'&gt;7&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Tools-for-samples-and-sampling&lt;/span&gt;"><span class="chapter-number">7</span> 
<span class="chapter-title">Tools for samples and sampling</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/probability_theory_1a.html&lt;span-class='chapter-number'&gt;8&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Probability-Theory,-Part-1&lt;/span&gt;"><span class="chapter-number">8</span> 
<span class="chapter-title">Probability Theory, Part 1</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/probability_theory_1b.html&lt;span-class='chapter-number'&gt;9&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Probability-Theory-Part-1-(continued)&lt;/span&gt;"><span class="chapter-number">9</span> 
<span class="chapter-title">Probability Theory Part 1
(continued)</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/more_sampling_tools.html&lt;span-class='chapter-number'&gt;10&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Two-puzzles-and-more-tools&lt;/span&gt;"><span class="chapter-number">10</span> 
<span class="chapter-title">Two puzzles and more tools</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/probability_theory_2_compound.html&lt;span-class='chapter-number'&gt;11&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Probability-Theory,-Part-2:-Compound-Probability&lt;/span&gt;"><span class="chapter-number">11</span> 
<span class="chapter-title">Probability Theory, Part 2: Compound
Probability</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/probability_theory_3.html&lt;span-class='chapter-number'&gt;12&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Probability-Theory,-Part-3&lt;/span&gt;"><span class="chapter-number">12</span> 
<span class="chapter-title">Probability Theory, Part 3</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/probability_theory_4_finite.html&lt;span-class='chapter-number'&gt;13&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Probability-Theory,-Part-4:-Estimating-Probabilities-from-Finite-Universes&lt;/span&gt;"><span class="chapter-number">13</span> 
<span class="chapter-title">Probability Theory, Part 4: Estimating
Probabilities from Finite Universes</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/sampling_variability.html&lt;span-class='chapter-number'&gt;14&lt;/span&gt;--&lt;span-class='chapter-title'&gt;On-Variability-in-Sampling&lt;/span&gt;"><span class="chapter-number">14</span> 
<span class="chapter-title">On Variability in Sampling</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/monte_carlo.html&lt;span-class='chapter-number'&gt;15&lt;/span&gt;--&lt;span-class='chapter-title'&gt;The-Procedures-of-Monte-Carlo-Simulation-(and-Resampling)&lt;/span&gt;"><span class="chapter-number">15</span> 
<span class="chapter-title">The Procedures of Monte Carlo Simulation
(and Resampling)</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/standard_scores.html&lt;span-class='chapter-number'&gt;16&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Ranks,-Quantiles-and-Standard-Scores&lt;/span&gt;"><span class="chapter-number">16</span> 
<span class="chapter-title">Ranks, Quantiles and Standard
Scores</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/inference_ideas.html&lt;span-class='chapter-number'&gt;17&lt;/span&gt;--&lt;span-class='chapter-title'&gt;The-Basic-Ideas-in-Statistical-Inference&lt;/span&gt;"><span class="chapter-number">17</span> 
<span class="chapter-title">The Basic Ideas in Statistical
Inference</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/inference_intro.html&lt;span-class='chapter-number'&gt;18&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Introduction-to-Statistical-Inference&lt;/span&gt;"><span class="chapter-number">18</span> 
<span class="chapter-title">Introduction to Statistical
Inference</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/point_estimation.html&lt;span-class='chapter-number'&gt;19&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Point-Estimation&lt;/span&gt;"><span class="chapter-number">19</span> 
<span class="chapter-title">Point Estimation</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/framing_questions.html&lt;span-class='chapter-number'&gt;20&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Framing-Statistical-Questions&lt;/span&gt;"><span class="chapter-number">20</span> 
<span class="chapter-title">Framing Statistical Questions</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/testing_counts_1.html&lt;span-class='chapter-number'&gt;21&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Hypothesis-Testing-with-Counted-Data,-Part-1&lt;/span&gt;"><span class="chapter-number">21</span> 
<span class="chapter-title">Hypothesis-Testing with Counted Data, Part
1</span></span> <span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/significance.html&lt;span-class='chapter-number'&gt;22&lt;/span&gt;--&lt;span-class='chapter-title'&gt;The-Concept-of-Statistical-Significance-in-Testing-Hypotheses&lt;/span&gt;"><span class="chapter-number">22</span> 
<span class="chapter-title">The Concept of Statistical Significance in
Testing Hypotheses</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/testing_counts_2.html&lt;span-class='chapter-number'&gt;23&lt;/span&gt;--&lt;span-class='chapter-title'&gt;The-Statistics-of-Hypothesis-Testing-with-Counted-Data,-Part-2&lt;/span&gt;"><span class="chapter-number">23</span> 
<span class="chapter-title">The Statistics of Hypothesis-Testing with
Counted Data, Part 2</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/testing_measured.html&lt;span-class='chapter-number'&gt;24&lt;/span&gt;--&lt;span-class='chapter-title'&gt;The-Statistics-of-Hypothesis-Testing-With-Measured-Data&lt;/span&gt;"><span class="chapter-number">24</span> 
<span class="chapter-title">The Statistics of Hypothesis-Testing With
Measured Data</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/testing_procedures.html&lt;span-class='chapter-number'&gt;25&lt;/span&gt;--&lt;span-class='chapter-title'&gt;General-Procedures-for-Testing-Hypotheses&lt;/span&gt;"><span class="chapter-number">25</span> 
<span class="chapter-title">General Procedures for Testing
Hypotheses</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/confidence_1.html&lt;span-class='chapter-number'&gt;26&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Confidence-Intervals,-Part-1:-Assessing-the-Accuracy-of-Samples&lt;/span&gt;"><span class="chapter-number">26</span> 
<span class="chapter-title">Confidence Intervals, Part 1: Assessing the
Accuracy of Samples</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/confidence_2.html&lt;span-class='chapter-number'&gt;27&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Confidence-Intervals,-Part-2:-The-Two-Approaches-to-Estimating-Confidence-Intervals&lt;/span&gt;"><span class="chapter-number">27</span> 
<span class="chapter-title">Confidence Intervals, Part 2: The Two
Approaches to Estimating Confidence Intervals</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/reliability_average.html&lt;span-class='chapter-number'&gt;28&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Some-Last-Words-About-the-Reliability-of-Sample-Averages&lt;/span&gt;"><span class="chapter-number">28</span> 
<span class="chapter-title">Some Last Words About the Reliability of
Sample Averages</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/correlation_causation.html&lt;span-class='chapter-number'&gt;29&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Correlation-and-Causation&lt;/span&gt;"><span class="chapter-number">29</span> 
<span class="chapter-title">Correlation and Causation</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/how_big_sample.html&lt;span-class='chapter-number'&gt;30&lt;/span&gt;--&lt;span-class='chapter-title'&gt;How-Large-a-Sample?&lt;/span&gt;"><span class="chapter-number">30</span> 
<span class="chapter-title">How Large a Sample?</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/bayes_simulation.html&lt;span-class='chapter-number'&gt;31&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Bayesian-Analysis-by-Simulation&lt;/span&gt;"><span class="chapter-number">31</span> 
<span class="chapter-title">Bayesian Analysis by
Simulation</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/references.htmlReferences">References</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:quarto-sidebar-section-1">Appendices</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/exercise_solutions.html&lt;span-class='chapter-number'&gt;A&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Exercise-Solutions&lt;/span&gt;"><span class="chapter-number">A</span> 
<span class="chapter-title">Exercise Solutions</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/technical_note.html&lt;span-class='chapter-number'&gt;B&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Technical-Note-to-the-Professional-Reader&lt;/span&gt;"><span class="chapter-number">B</span> 
<span class="chapter-title">Technical Note to the Professional
Reader</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/acknowlegements.html&lt;span-class='chapter-number'&gt;C&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Acknowledgements&lt;/span&gt;"><span class="chapter-number">C</span> 
<span class="chapter-title">Acknowledgements</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/code_topics.html&lt;span-class='chapter-number'&gt;D&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Code-topics&lt;/span&gt;"><span class="chapter-number">D</span> 
<span class="chapter-title">Code topics</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-int-sidebar:/errors_suggestions.html&lt;span-class='chapter-number'&gt;E&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Errors-and-suggestions&lt;/span&gt;"><span class="chapter-number">E</span> 
<span class="chapter-title">Errors and suggestions</span></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-breadcrumbs-&lt;span-class='chapter-number'&gt;7&lt;/span&gt;--&lt;span-class='chapter-title'&gt;Tools-for-samples-and-sampling&lt;/span&gt;"><span class="chapter-number">7</span> 
<span class="chapter-title">Tools for samples and sampling</span></span>
</div>
<div class="hidden" id="quarto-meta-markdown">
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-metatitle"><span class="quarto-section-identifier" id="sec-sampling-tools"><span class="chapter-number">7</span> 
<span class="chapter-title">Tools for samples and sampling</span></span>
– Resampling statistics</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-twittercardtitle"><span class="quarto-section-identifier" id="sec-sampling-tools"><span class="chapter-number">7</span> 
<span class="chapter-title">Tools for samples and sampling</span></span>
– Resampling statistics</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-ogcardtitle"><span class="quarto-section-identifier" id="sec-sampling-tools"><span class="chapter-number">7</span> 
<span class="chapter-title">Tools for samples and sampling</span></span>
– Resampling statistics</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-metasitename">Resampling statistics</span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-twittercarddesc"></span>
<span class="hidden quarto-markdown-envelope-contents" render-id="quarto-ogcardddesc"></span>
</div>
